\documentclass[a4paper,12pt,twoside,openright]{book} 
\input{Includes.tex}
\input{colors.tex}

\addto\extrasenglish{%
  \renewcommand{\chapterautorefname}{Chapter}%
  \renewcommand{\sectionautorefname}{Section}%
}

\hyphenation{fi-gu-re}
\hyphenation{le-gend}
\hyphenation{i-ma-ges}
\hyphenation{i-ma-ge}
\hyphenation{va-lues}
\hyphenation{va-lue}
\hyphenation{bet-ween}
\hyphenation{a-chie-ving}


\pagenumbering{Roman} 

\title{Automatic Interpretation of Map Visualizations with Color-encoded Scalar Values from \\Bitmap Images}
\author{Angela Gabriela Mayhua Quispe}
\orientador{PhD. Jorge Poco}
\jurado
{
%\\ Dr. David Menotti -- Universidade Federal do Paraná  -- Brasil
%\\ Dr. Juan Carlos Gutierrez -- Universidad Católica San Pablo -- Perú
%\\ Dr. Erick Gomez Nieto -- Universidade de Sao Paulo -- Brasil
%\\ Dr. Alex Cuadros Vargas -- Universidad Católica San Pablo -- Perú
}

\dedicado{
%Aquí deberás colocar a quien va dedicada tu tesis por ejemplo: A Dios, por todo lo que me ha dado, a todos los profesores por sus enseñanzas y algunos amigos.
To my parents, Santos and Marina, who never stop giving of themselves in countless ways.
To my brothers and sister, who encourage and support me.
}

\begin{document}
\maketitle 

\include{abbreviations}
\input{acknowledgments}
\input{abstract_en}
\input{abstract_es} 

\tableofcontents 
\listoftables 
\addcontentsline{toc}{chapter}{List of Tables}
%\cleardoublepage
\listoffigures 
\addcontentsline{toc}{chapter}{List of Figures}
%\listoftables 
%\listoffigures 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%   En esta parte deberas incluir los archivos de tu tesis   %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage 
\pagenumbering{arabic} 


\input{figures}	% contain all images
\input{ch_intro}
\input{ch_relatedWorks}
\input{ch_background}

\chapter{Automatic Interpretation of Map Visualizations}
\label{ch:proposal}
Our work is based on the application of \textit{reverse engineering} to bitmap images of map visualizations to recover their visual encodings in \ac{JSON} format. To achieve this goal, we extract the spatial and color information from a map visualization image using different techniques, which are presented in this chapter.
%
Section x describes our corpus and how it was generated. Section y presents an overview of our work. Sections v, w and z detail the techniques used to extract spatial and color information; in addition, each one presents the evaluation results. Finally, Section m details how the visual encoding is inferred using the information of previous steps.


\input{ch_conclusions}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\bibliographystyle{apalike}
\bibliographystyle{apabrahand}
\bibliography{thesis-doc}
\addcontentsline{toc}{chapter}{Bibliography}

\end{document}