    \chapter{Introduction}
    %\label{ch:intro}
    % In \autoref{sec:motivation} we describe the motivation and context of our work, \autoref{sec:problem} presents our problem statement. \autoref{sec:objectives} shows the objectives of this work. Finally, \autoref{sec:outline} describes the structure of this thesis document.
    \section{Motivation and Context}
    %\label{sec:motivation}
    %%%TODO: FALTA MAS TEXTO EN LA MOTIVATION

    Switched systems are widely used in engineering applications and its 
    importance has grown up considerably these last years, because of their 
    ease of implementation for controlling cyber-physical systems.
    A switched systems is a set of dynamical systems, each with its own 
    dynamical behaviour controlled by a parameter mode $u$ whose values 
    are in a finite set $U$(See ~\cite{liberzon2003switching}). However, due to the composition of many switched systems together, the global switched systems has a number of modes and dynamics which increases exponentially. 
    Switched systems have numerous applications in control of mechanical systems, the automotive industry, and many other fields. 

    \section{Problem Statement}
    %\label{sec:problem}
    Nowadays, there is a large number of methods to solve switched systems;
    however, it does not have guarantee in safety. For that reason, we 
    propose a new approach to solve switched systems. 
    
    \section{Objectives}
    %\label{sec:objectives}

        \subsection*{General Objective}
        Our main objective is to propose a pipeline to solve switched systems guarantee safety and optimal synthesis controllers. 

        \subsection*{Specific Objectives}
        To achieve our main objective, we have the following specific objectives:
        \begin{itemize}
            \item Define a case of study and get its mathematical model.
            \item Implement a safety controller for switched systems.
            \item Optimize the switched systems using model checking techniques.
            \item Evaluate each step of the pipeline and compare with traditional approaches.
        \end{itemize}


    \section{Contributions}
        This thesis proposes a novel approach to solve switched systems guaranteeing safety and optimal controller synthesis. This procedure to consider stochastic variables as an input for the system. Our contributions are related to each part and are detailed below.

        \begin{itemize}%\usepackage[spanish, es-ucroman]{babel}}
        \item Define %\usepackage[spanish, es-ucroman]{babel}a synthesis controller with the next:.
        %\usepackage[spanish, es-ucroman]{babel}
        \begin{itemize}%\usepackage[spanish, es-ucroman]{babel}e}
        \item We propose a method to guarantee safe controller. This methods consider three regions to have reachability and safety in the system.
        \item We also demonstrate the utility of the proposed method comparing with traditional methods.
        \end{itemize}
        \item Analyze the stability for our case of study study.
        \begin{itemize}
        \item analyze the zeros and poles for the system.
        \end{itemize}
        \end{itemize}
    \section{Outline}
    %\label{sec:outline}
    %This thesis document is divided into six chapters. After this introduction and problem formulation, in \autoref{ch:relatedWorks} we survey the literature about the recent research in safety controllers and optimal controller synthesis. 
    %\autoref{ch:background} presents some basic concepts about the dynamical systems, traditional controllers, switched systems,stability criteria and optimal controller technique. Next, in Chapter x we describe in detail the corpus, techniques used by our pipeline and their evaluation results. Finally, the limitations, future works, and conclusions of this work are presented in Chapter z.
