
\chapter{Related Works}
\label{ch:relatedWorks}

Our work draws on prior research in the areas of hybrid systems, safe patterns
and online control synthesis.

\section{Online and Compositional Learning of Controllers with Application to Floor Heating}
    \label{sec:onlinefloorheating}
    This work has proposed one method to perform \textit{optimal controller 
    synthesis for stochastic hybrid games} \ac{SHG} e.g. a  floor heating 
     system in a house \cite{larsen2016online}. 
    Is proposed a general and scalable methodology for controller synthesis 
    for such systems. Instead of off-line synthesis of a controller for 
    all possible input temperatures and an arbitrary time horizon, is 
    proposed an on-line synthesis methodology, where  it periodically 
    compute the controller only for the near future based on the 
    current sensor readings. \textsc{uppaal}, is an integrated tool environment 
    for modelling, validation and verification of real-time systems modeled as 
    networks of  timed automata, extended with data types. \textsc{stratego} 
    facilitates generation, optimization, comparison as well as consequence and
    performance exploration of strategies for stochastic priced timed games
    in a user-friendly manner. The online approach may be seen as a instance 
    of model predictive control \ac{MPC} or receding time horizon control for hybrid 
    systems. The application of \ac{MPC} to hybrid systems subject to disturbances or 
    uncertainties gives rises to uncertain optimization problems. Many robust 
    \ac{MPC} schemes are based on the min-max strategy originally.

\section{An Improved Algorithm for the Control Synthesis of Nonlinear Sampled Switched Systems}
    \label{sec:safealgorithm}
    In this paper is presented and algorithm for the control synthesis for
    nonlinear \ac{SS} using and existing procedure of state-space 
    and made available for nonlinear systems with the help of guaranteed 
    integration, the algorithm has been improved to be able to consider longer 
    patterns of modes with a better running approach. This approach permits 
    to deal with stability, reachability, safety and forbidden region 
    constraints. The approach was numerically validated
    on several examples taken from the literature \cite{le2017improved}. Additionally, the search of patterns that guarantee 
    stability, reachability and safety is given by an \emph{decomposition}
    and \emph{find patterns} algorithms; the decomposition algorithm 
    divide each box in small box in order to find pattern that 
    satisfy stability definition at \autoref{sec:safepatterncomputation}. 
    This methods are widely discussed in \citep{fribourg2014finite} for instance 
    operators such as $Post_{\pi_i}(X)$ and $Tube_{ \pi_i}(X)$ that determine 
    the state after $\tau$ time and sequences of states to reach $Post_{\pi_i}(X)$ 
    respectively. Some applications are also proposed the boost DC-DC converter,
    helicopter motion, two-room building heating and multilevel converter.
    The control with disturbances is one of the very interesting features 
    in the algorithm due to is only necessary replace the disturbances with
    an interval with its respective zonotope to get the pattern. The zonotope
    is an small region that was divided with the objective to verify 
    stability and safety, these zonotopes was proposed to as polytopes with
    several interesting properties: these can be encoded efficiently, 
    \emph{stability} property require \emph{reachibility} property which is 
    discussed and analized in \citep*{girard2005reachability}

    

    
    


% \section{Distributed Synthesis of State-Dependent Switching Control}
%     \label{sec:distributedsynthesis}
%     In this part is presented a correct-by-design method of state-dependent control
%     synthesis for linear discrete-time switching systems. Given an objective region 
%     R of the state space, the method builds a region S. \cite{le2016distributed}


\section{Final Considerations}
    This chapter presented some recent proposals related to our thesis work. Some research works have been focused on analyzing safety controller over switched systems. On the other hand, other works have focused on optimize controller synthesis using some techniques related to model checking. 
    The next chapter will present some concepts needed to understand better our work, those concepts are related to the modelling physical system over our case of study and represent as a state space.


















